Partitioned Local Depth (PaLD) Community Analyses in R

### 2023-05-02 r-journal/dagostino-mcgowan.Rmd
update abstract
capitalize cluster

---
title: "Partitioned Local Depth (PaLD) Community Analyses in R"
author:
  - name: Lucy D'Agostino McGowan
    affiliation: Wake Forest University
    address:
    - Winston-Salem, NC
    - 27106
    email:  mcgowald@wfu.edu
  - name: Katherine Moore
    affiliation: Wake Forest Unversity
    address:
    - Winston-Salem, NC
    - 27106
    email: mooreke@wfu.edu 
  - name: Kenneth Berenhaut 
    affiliation: Wake Forest University
    address:
    - Winston-Salem, NC
    - 27106
    email: berenhks@wfu.edu 
abstract: >
  Partitioned Local Depth (PaLD) is a framework for a holistic consideration of the community structure of distance-based data. This paper describes an R package, \CRANpkg{pald}, for calculating Partitioned Local Depth (PaLD) probabilities, implementing community analyses, and creating data visualizations to display community structure. We describe how to use the package as well as walk through several examples. 
output: rticles::rjournal_article
---

@@

In this example, three clusters are identified with these six points. Points `A`, `B`, and `E` fall into cluster 1. Point `C` is in cluster 2 (a cluster of size 1) and points `D` and `F` fall into cluster 3.

@@

From this, we can glean that cluster 1 consists of two types of tissue, the kidney and endometrium. Cluster 2 is comprised of only the hippocampus.

>>>>

---
title: "Partitioned Local Depth (PaLD) Community Analyses in R"
author:
  - name: Lucy D'Agostino McGowan
    affiliation: Wake Forest University
    address:
    - Winston-Salem, NC
    - 27106
    email:  mcgowald@wfu.edu
  - name: Katherine Moore
    affiliation: Wake Forest Unversity
    address:
    - Winston-Salem, NC
    - 27106
    email: mooreke@wfu.edu 
  - name: Kenneth Berenhaut 
    affiliation: Wake Forest University
    address:
    - Winston-Salem, NC
    - 27106
    email: berenhks@wfu.edu 
abstract: >
  Partitioned Local Depth (PaLD) is a framework for a holistic consideration of the community structure of distance-based data. This paper describes an R package, \CRANpkg{pald}, for calculating Partitioned Local Depth (PaLD) probabilities, implementing community analyses, and creating data visualizations to display community structure. We describe how to use the package, walk through several examples, and contrast the results with commonly used techniques. 
output: rticles::rjournal_article
---

@@

In this example, three clusters are identified with these six points. Points `A`, `B`, and `E` fall into Cluster 1. Point `C` is in Cluster 2 (a cluster of size 1) and points `D` and `F` fall into Cluster 3.

@@

From this, we can glean that Cluster 1 consists of two types of tissue, the kidney and endometrium. Cluster 2 is comprised of only the hippocampus.

### 2023-05-02 r-journal/dagostino-mcgowan.tex
capitalize cluster

\begin{Schunk}
\begin{Sinput}
graphs <- community_graphs(cohesion)
graphs[["G_strong"]]
\end{Sinput}
\begin{Soutput}
#> IGRAPH 9daec2b UNW- 6 3 -- 
#> + attr: name (v/c), weight (e/n)
#> + edges from 9daec2b (vertex names):
#> [1] A--B A--E D--F
\end{Soutput}
\end{Schunk}

@@

In this example, three clusters are identified with these six points.
Points \texttt{A}, \texttt{B}, and \texttt{E} fall into cluster 1. Point
\texttt{C} is in cluster 2 (a cluster of size 1) and points \texttt{D}
and \texttt{F} fall into cluster 3.

@@

\begin{Schunk}
\begin{Sinput}
french_neighbors <- igraph::neighbors(cognate_graph_strong, "French")
french_neighbors
\end{Sinput}
\begin{Soutput}
#> + 8/87 vertices, named, from 8f39182:
#> [1] Italian         Ladin           Provencal       Walloon        
#> [5] French_Creole_C French_Creole_D Spanish         Catalan
\end{Soutput}
\end{Schunk}

>>>>

\begin{Schunk}
\begin{Sinput}
graphs <- community_graphs(cohesion)
graphs[["G_strong"]]
\end{Sinput}
\begin{Soutput}
#> IGRAPH e4c9a8b UNW- 6 3 -- 
#> + attr: name (v/c), weight (e/n)
#> + edges from e4c9a8b (vertex names):
#> [1] A--B A--E D--F
\end{Soutput}
\end{Schunk}

@@

In this example, three clusters are identified with these six points.
Points \texttt{A}, \texttt{B}, and \texttt{E} fall into Cluster 1. Point
\texttt{C} is in Cluster 2 (a cluster of size 1) and points \texttt{D}
and \texttt{F} fall into Cluster 3.

@@

\begin{Schunk}
\begin{Sinput}
french_neighbors <- igraph::neighbors(cognate_graph_strong, "French")
french_neighbors
\end{Sinput}
\begin{Soutput}
#> + 8/87 vertices, named, from 81f58d9:
#> [1] Italian         Ladin           Provencal       Walloon        
#> [5] French_Creole_C French_Creole_D Spanish         Catalan
\end{Soutput}
\end{Schunk}
